Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-15 paper/conclusion.tex
Minor edits.

%The task of automatic cell boundary segmentation is difficult, and trying to improve such segmentations automatically as a post-process through merge and split error correction is, in principle, no different than trying to improve the underlying cell boundary segmentation. Due to the task difficulty, manual proofreading of connectomics segmentations is necessary, but it is a time consuming and error-prone task. Humans are the bottleneck and minimizing the manual labor is the goal.
In this paper, we have trained classifiers to find merge and split errors in automatic segmentations of connectomics data. We then reduce the correction of these errors to simple yes/no decisions. This allows proofreading with better performance than existing systems.
Our experiments also show that automatic proofreading works. This has the potential to further reduce the manual labor and will be the target of future research. To encourage testing of our proposed architecture and replicate our experiments, we provide our framework and data as free and open research at (link omitted for review).

>>>>

%The task of automatic cell boundary segmentation is difficult, and trying to improve such segmentations automatically as a post-process through merge and split error correction is, in principle, no different than trying to improve the underlying cell boundary segmentation. Due to the task difficulty, manual proofreading of connectomics segmentations is necessary, but it is a time consuming and error-prone task. Humans are the bottleneck and minimizing the manual labor is the goal.
In this paper, we have trained classifiers to find merge and split errors in automatic segmentations of connectomics data. We then reduce the correction of these errors to simple yes/no decisions. This allows proofreading with better performance than existing systems.
Our experiments also show that automatic proofreading works. This has the potential to further reduce the manual labor and will be the target of future research. To encourage testing of our proposed architecture and replication of our experiments, we provide our framework and data as free and open research at (link omitted for review).

### 2016-11-15 paper/evaluation.tex
Results section complete.
Minor edits.

Table~\ref{tab:parameters} lists the final parameters. Our CNN configuration results in approximately 170,000 learnable parameters. We assume that training has converged if the validation loss does not decrease for 50 epochs. We test the CNN by generating a balanced set of 8,780 correct and 8,780 error patches using unseen data of the left cylinder dataset.

@@

\paragraph{Computer-aided proofreading.} We compare against focused proofreading by Plaza~\cite{focused_proofreading}. Focused proofreading performs graph analysis on the output from NeuroProof~\cite{neuroproof2013}, instead of our GALA approach. Therefore, for training our focused proofreading baseline, we replace GALA in our automatic segmentation pipeline with NeuroProof but use exactly the same input data including membrane probabilities. We obtained the best possible parameters for NeuroProof by consulting the developers (Table~\ref{tab:parameters}). Rather than using Raveler as the frontend, we use our own interface (Fig.~\ref{fig:ui}) to compare only the classifier part of Plaza's approach.

@@

\paragraph{Novice study design.} We recruited participants with no experience in electron microscopy data or proofreading, through flyers, mailing lists, and personal interaction. Based on sample size calculation theory, we estimated the study needed ten users per proofreading tool including four potential dropouts~\cite{samplesize1,samplesize2}. All twenty participants completed the study ($N=20$, 10 female; 19-65 years old, $M$=30).

Each study session began with a five minute standardized explanation of the task. Then, the participants were asked to perform a 3 minute proofreading task on separate but representative data using focused proofreading. The participants were allowed to ask questions during this time. The classifier did not matter in this case since the user interface was the same. The experimenter then loaded the AC4 subvolume with initial pre-computed classifications by either guided proofreading or focused proofreading depending on assignment. After 30 minutes, the participants completed the raw NASA-TLX standard questions for task evaluation~\cite{NASATLX}.
\begin{figure*}[t]
\begin{center}
\includegraphics[width=\linewidth]{gfx/ac4trails.pdf}
\end{center}
  \vspace{-4mm}
   \caption{Performance comparison of focused proofreading by Plaza and our guided proofreading methods on the AC4 subvolume. All measurements are reported as median VI, the lower the better. We compare different approaches of accepting or rejecting corrections for each method: automatic selection with threshold (indicated by the red line), forced choice by ten novice users, forced choice by two domain experts, and the selection oracle. In all cases, guided proofreading yields better results with less corrections.}
\label{fig:ac4trails}
\end{figure*}
\paragraph{Expert study design.} We recruited 4 domain experts to evaluate the performance of both guided and focused proofreading. We obtained study consent and randomly assigned 2 experts to proofread using each classifier. The experts performed the 3 minute test run on different data prior to proofreading for 30 minutes. After the task ended, the experts were asked to complete the raw NASA-TLX questionnaire.

\paragraph{Evaluation metric.} For each experiment, we measure the similarity between proofread segmentations and the manual `ground truth' labelings using \textit{variation of information} (VI). VI is a measure of the distance between two clusterings, closely related to mutual information, where lower means better. We treat VI as a continuous variable during analysis.

>>>>

Table~\ref{tab:parameters} lists the final parameters. Our CNN configuration results in 171,474 learnable parameters. We assume that training has converged if the validation loss does not decrease for 50 epochs. We test the CNN by generating a balanced set of 8,780 correct and 8,780 error patches using unseen data of the left cylinder dataset.

@@

\paragraph{Computer-aided proofreading.} We compare against focused proofreading by Plaza~\cite{focused_proofreading}. Focused proofreading performs graph analysis on the output from NeuroProof~\cite{neuroproof2013}, instead of our GALA approach. Therefore, for training our focused proofreading baseline, we replace GALA in our automatic segmentation pipeline with NeuroProof but use exactly the same input data including membrane probabilities. We obtained the best possible parameters for NeuroProof by consulting the developers (Table~\ref{tab:parameters}). Rather than using Raveler as the frontend, we use our own interface (Fig.~\ref{fig:ui}) to compare only the classifier from Plaza's approach.

@@

\paragraph{Novice study design.} We recruited participants with no experience in electron microscopy data or proofreading through flyers, mailing lists, and personal interaction. Based on sample size calculation theory, we estimated the study needed ten users per proofreading tool including four potential dropouts~\cite{samplesize1,samplesize2}. All twenty participants completed the study ($N=20$, 10 female; 19-65 years old, $M$=30).

Each study session began with a five minute standardized explanation of the task. Then, the participants were asked to perform a 3 minute proofreading task on separate but representative data using focused proofreading. The participants were allowed to ask questions during this time. The classifier did not matter in this case since the user interface was the same. The experimenter then loaded the AC4 subvolume with initial pre-computed classifications by either guided proofreading or focused proofreading depending on assignment. After 30 minutes, the participants completed the raw NASA-TLX standard questions for task evaluation~\cite{NASATLX}.
\begin{figure*}[t]
\begin{center}
\includegraphics[width=\linewidth]{gfx/ac4trails.pdf}
\end{center}
  \vspace{-4mm}
   \caption{Performance comparison of Plaza's focused proofreading and our guided proofreading methods on the AC4 subvolume. All measurements are reported as median VI, the lower the better. We compare different approaches of accepting or rejecting corrections for each method: automatic selection with threshold (indicated by the red line), forced choice by ten novice users, forced choice by two domain experts, and the selection oracle. In all cases, guided proofreading yields better results with fewer corrections.}
\label{fig:ac4trails}
\end{figure*}
\paragraph{Expert study design.} We recruited 4 domain experts to evaluate the performance of both guided and focused proofreading. We obtained study consent and randomly assigned 2 experts to proofread using each classifier. The experts performed the 3 minute test run on different data prior to proofreading for 30 minutes. After the task ended, the experts were asked to complete the raw NASA-TLX questionnaire.

\paragraph{Evaluation metric.} For each experiment, we measure the similarity between proofread segmentations and the manual `ground truth' labelings using \textit{variation of information} (VI). VI is a measure of the distance between two clusterings, closely related to mutual information, where lower means a better match to ground truth. We treat VI as a continuous variable during analysis.

### 2016-11-15 paper/results.tex
Add explanation.
Minor edits.

\paragraph{L. Cylinder.} Evaluation was performed on previously unseen sections of mouse cortex volume of Kasthuri~\etal~\cite{kasthuri2015saturated}. We generated an unbalanced dataset of 81,184 correct and 8,780 split error patches in respect to the ground truth labeling. We then ranked each patch using focused proofreading and guided proofreading and compared precision/recall (Table \ref{tab:prcyl}. Our method exhibits higher precision and recall for correct and error patches.

@@

\subsection{Forced Choice User Experiment}
We performed a user study to evaluate the forced choice error correction method among novices and experts. To be comparable to Haehn's~\etal Dojo user study, participants were asked to proofread the AC4 subvolume for 30 minutes. We counted 10 merge errors and 322 split errors by computing the maximum overlap of the initial segmentation in respect to the ground truth labeling (both provided by Haehn~\etal). For evaluation, we measure the performance of proofreading quantitatively by comparing VI scores of segmentations to ground truth. The median VI of the initial segmentation was 0.476 (SD=0.089). Most novices and all experts were able to improve upon this score with both, focused proofreading and guided proofreading (Fig.~\ref{fig:ac4trails}).

\paragraph{Novice performance.} Participants using focused proofreading were able to reduce the median VI of the automatic segmentation to $0.469$ ($SD=0.87$). On average, users viewed $423.4$ corrections and accepted $45.8$ of them with an average time of $4.9$ seconds spent per correction. Participants using guided proofreading were able to reduce the median VI to $0.424$ ($SD=0.037$). Here, users viewed on average $353.4$ corrections and accepted $106.9$ in $6.2$ seconds. While three users of focused proofreading made the initial segmentation worse, all participants using guided proofreading were able to improve it. In comparison to the results of Haehn~\etal, focused and guided proofreading outperform interactive proofreading with Dojo (median VI $0.535$, $SD=0.055$). The slope of VI score per correction in Fig.~\ref{fig:ac4trails} shows that guided proofreading enables improvements with fewer corrections than the other tools. Interestingly, novice performance decreases after approximately $300$ corrections. There are two explanations for this: user fatigue and increasing uncertainty during error suggestion from the classifier. Regarding fatigue, we suggest for future experiments to add short breaks after every ten minutes.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
\end{center}
  \vspace{-4mm}
   \caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across the AC4 subvolume with different error correction approaches. The performance of focused proofreading with automatic selection is an order of magnitude higher (as indicated by the arrow) and is reported in the text.}
\label{fig:ac4boxplot}
\end{figure}
\subsection{Automatic Error Correction}

\paragraph{Selection oracle.} Accepting and rejecting proofreading corrections with the selection oracle yields the best performance on all datasets because all detected merge and split are corrected as long as the segmentation is improved. Fig.~\ref{fig:ac4trails} shows slope of VI reduction using the selection oracle on the AC4 subvolume (initial median VI $0.476$, $SD=0.089$). With focused proofreading, the selection oracle reaches a median VI of $0.353$ ($SD=0.037$) after $1605$ corrections. With guided proofreading, the oracle results in a median VI of $0.342$ ($SD=0.03$) after approximately $800$ corrections and then stagnates until all regions are proofread. Both results are very close to the best possible median VI of $0.334$ (calculated by computing maximum overlap with the ground truth). The slope of the trails in Fig.~\ref{fig:ac4trails} shows that guided proofreading requires less corrections to reach a reasonable reduction in VI. Fig.~\ref{fig:ac4boxplot} shows the VI distribution across methods.
The results on the L. Cylinder dataset (initial VI $0.379$, $SD=0.118$) are similar: Focused proofreading reduces the median VI to $0.298$ ($SD=0.075$) after $26,170$ corrections ($2,419$ accepted). Guided proofreading reduces the median VI to $0.2996$ ($SD=0.073$) after $27,491$ corrections ($2,696$ accepted).

@@

\paragraph{Merge Error Detection} Guided proofreading performs merge error detection prior to split error detection. The classifier automatically found 10 merge errors in the AC4 subvolume of which 4 reduce VI . Automatic selection with $p_t=0.95$ corrected all of these 4 true errors and in addition 2 false ones (precision/recall 0.67/1.00, f1-score 0.80). In 50 sections of the L. Cylinder dataset 151 merge errors were automatically found of which 17 reduce VI. Automatic selection with $p_t=0.95$ corrected 6 true errors and 30 false ones (precision/recall 0.17/0.35, f1-score 0.23). \DFH{Not good. The split error correction cleans up but still not good, might be bug. hard to track down on the large data.}

>>>>

\paragraph{L. Cylinder.} Evaluation was performed on previously unseen sections of mouse cortex volume of Kasthuri~\etal~\cite{kasthuri2015saturated}. We generated an unbalanced dataset of 81,184 correct and 8,780 split error patches in respect to the ground truth labeling. We then ranked each patch by using focused proofreading, guided proofreading and compared precision/recall (Table \ref{tab:prcyl}. Our method exhibits higher precision and recall for correct and error patches.

@@

\subsection{Forced Choice User Experiment}
We performed a user study to evaluate the forced choice error correction method among novices and experts. To be comparable to Haehn's~\etal Dojo user study, participants were asked to proofread the AC4 subvolume for 30 minutes. We counted 10 merge errors and 322 split errors by computing the maximum overlap of the initial segmentation with respect to the ground truth labeling (both provided by Haehn~\etal). For evaluation, we measure the performance of proofreading quantitatively by comparing VI scores of segmentations relative to ground truth. The median VI of the initial segmentation was 0.476 (SD=0.089). Most novices and all experts were able to improve upon this score with both, focused proofreading and guided proofreading (Fig.~\ref{fig:ac4trails}).

\paragraph{Novice performance.} Participants using focused proofreading were able to reduce the median VI of the automatic segmentation to $0.469$ ($SD=0.87$). On average, users viewed $423.4$ corrections and accepted $45.8$ of them with an average time of $4.9$ seconds spent per correction. Participants using guided proofreading were able to reduce the median VI to $0.424$ ($SD=0.037$). Here, users viewed on average $353.4$ corrections and accepted $106.9$ in $6.2$ seconds. While three users of focused proofreading made the initial segmentation worse, all participants using guided proofreading were able to improve it. In comparison to the results of Haehn~\etal, focused and guided proofreading outperform interactive proofreading with Dojo (median VI $0.535$, $SD=0.055$). The slope of VI score per correction in Fig.~\ref{fig:ac4trails} shows that guided proofreading enables improvements with fewer corrections than the other tools. Interestingly, novice performance decreases after approximately $300$ corrections. There are two explanations for this: user fatigue and increasing uncertainty during error suggestion from the classifier. Regarding fatigue, we suggest future experiments short breaks after every ten minutes.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
\end{center}
  \vspace{-4mm}
   \caption{VI distributions of guided proofreading (GP), focused proofreading (FP) and Dojo output across the AC4 subvolume with different error correction approaches. The variation resulting from performance of focused proofreading with automatic selection is an order of magnitude higher (as indicated by the arrow) and is reported in the text.}
\label{fig:ac4boxplot}
\end{figure}
\subsection{Automatic Error Correction}

\paragraph{Selection oracle.} Accepting and rejecting proofreading corrections with the selection oracle yields the best performance on all datasets because all detected merge and split errors are corrected as long as the segmentation is improved. Fig.~\ref{fig:ac4trails} shows slope of VI reduction using the selection oracle on the AC4 subvolume (initial median VI $0.476$, $SD=0.089$). With focused proofreading, the selection oracle reaches a median VI of $0.353$ ($SD=0.037$) after $1605$ corrections. With guided proofreading, the oracle results in a median VI of $0.342$ ($SD=0.03$) after approximately $800$ corrections and then stagnates until all regions are proofread. Both results are very close to the best possible median VI of $0.334$ (calculated by computing maximum overlap with the ground truth). The slope of the trails in Fig.~\ref{fig:ac4trails} shows that guided proofreading requires fewer corrections to reach a reasonable reduction in VI. Fig.~\ref{fig:ac4boxplot} shows the VI distribution across methods.
The results on the L. Cylinder dataset (initial VI $0.379$, $SD=0.118$) are similar. Focused proofreading reduces the median VI to $0.298$ ($SD=0.075$) after $26,170$ corrections ($2,419$ accepted). Guided proofreading reduces the median VI to $0.2996$ ($SD=0.073$) after $27,491$ corrections ($2,696$ accepted).

@@

\paragraph{Merge Error Detection} Guided proofreading performs merge error detection prior to split error detection. The classifier found 10 merge errors in the AC4 subvolume of which 4 reduce VI. Automatic selection with $p_t=0.95$ corrected 6 of these errors (precision/recall 0.87/0.80, f1-score 0.80). This was not captured in median VI but resulted in a mean VI reduction from $0.512$ ($SD=0.09$) to $0.509$ ($SD=0.086$). The selection oracle reduced mean VI with only merge errors to $0.508$ ($SD=0.086$). In the forced choice user study, participants marked 1.9 merge errors (experts: 2) merge errors for correction and reduce mean VI to $0.502$ (experts: VI $0.503$, $SD=0.086$). This shows how hard it is to identify merge errors and how little they effect VI. In 50 sections of the L. Cylinder dataset 151 merge errors were automatically found of which 17 reduce VI. Automatic selection with $p_t=0.95$ corrected 6 true VI-reducing errors and 30 VI-increasing ones (precision/recall 0.82/0.73, f1-score 0.77) without - in sum - any effect on the VI.
